\documentclass[10pt,floatfix,a4paper]{article}
\usepackage{mathrsfs,amsfonts,amssymb,amsmath}
\usepackage[normalem]{ulem}
\usepackage{graphicx}
\usepackage[linktocpage,breaklinks]{hyperref}
\usepackage[capitalize]{cleveref}
\usepackage[usenames,dvipsnames]{xcolor}
\hypersetup{colorlinks=true,
            citecolor=NavyBlue,
            linkcolor=magenta,
            urlcolor=magenta}
\usepackage{multirow,array}
\DeclareMathAlphabet{\pazocal}{OMS}{zplm}{m}{n}

\usepackage{wrapfig}
\usepackage[capitalize]{cleveref}
\usepackage[legalpaper, top=1in, bottom=1in, right=1in, left=.7in]{geometry}
%\usepackage[symbol]{footmisc} % activate the use of * for electronic address

\usepackage[sorting=none,style=numeric-comp,natbib]{biblatex}
\addbibresource{references.bib}

\newcommand{\hk}[1]{\textcolor{Violet}{#1}}

\usepackage{eurosym}
%\linespread{1}
%\pagestyle{plain}

\begin{document}
\begin{center}
  {\LARGE \bf CURRICULUM VITAE} \\[2ex]
  {\Large \bf Hao-Jui Kuan}
\end{center}

%\vspace{5mm}

\section*{Personal information}
\begin{tabbing}
  \hspace*{5mm} \= \hspace*{2.3cm} \= \hspace*{10cm} \\[-3ex]
  \> Date of birth\hspace{1.2mm}:  \> 13 July 1995\\
  \> Nationality\hspace{4mm}: \> Taiwan\\
  \> Email/web\hspace{4.3mm}: \> hao-jui.kuan@aei.mpg.de, \href{https://hao-jui.github.io}{\textcolor{magenta}{hao-jui.github.io}}\\
  \> Address\hspace{8.7mm}: \> Albert-Einstein-Institut, Am M{\"u}hlenberg 1, 14476 Potsdam
\end{tabbing}


\section*{Professional experience}
\begin{tabbing}
  \hspace*{5mm} \= \hspace*{2.3cm} \= \hspace*{10cm} \\[-3ex]
  \> 2023 - \> Postdoc in the Computational Relativistic Astrophysics division at the Max Planck Institute \\
  \> \> for Gravitational Physics (Albert Einstein Institute)
\end{tabbing}

\section*{Education}
\begin{tabbing}
  \hspace*{5mm} \= \hspace*{2.3cm} \= \hspace*{10cm} \\[-3ex]
  \> 2019 - 2022 \>  University of T{\"u}bingen, T\"ubingen, Germany. \textit{Advisor: Kostas D.~Kokkotas} \\
  \> \> Ph.D. in Theoretical Astrophysics.  Summa Cum Laude (excellent; about 1 in 50 graduates). \\[1ex]
  \> 2017 - 2022 \> National Tsing Hua University, Taiwan. \textit{Advisor: Chao-Qiang Geng} \\
  \> \> PhD in Physics (joint degree). \\[1ex]
  \> 2013 - 2017 \> National Tsing Hua University, Taiwan. \\
  \> \> B.Sc Double major in Physics and Mathematics.
\end{tabbing}

%\section*{Referee activity}
%\section*{Research interest}
%\begin{itemize}
%    \item Evolutionary study of the pre-merger dynamics of magnetized neutron stars 
%    \item Dynamical aspects of compact objects in alternative theories
%    \item Quasi-normal mode asteroseismology via universal relations, and tidal effects in binaries
%\end{itemize}

\section*{Honors and Awards}
\begin{tabbing}
  \hspace*{5mm} \= \hspace*{2.3cm} \= \hspace*{10cm} \\[-3ex]
  \> 2023\> Honorable Mention in the Gravitational Wave International Committee (GWIC)-\href{https://gwic.ligo.org/thesis-prize.html}{Braccini Thesis Prize} \\
  \> 2023\> Dr. Friedrich F{\"o}rster Prize, one awardee in Faculty of Science in University of T{\"u}bingen, \euro{1,000}. \\
  \> 2023\> Student Outstanding Paper Award from NCTS (Taiwan), converted as $\sim620$~USD.
\end{tabbing}



\section*{Funded Grant Activity}
\begin{tabbing}
  \hspace*{5mm} \= \hspace*{2.3cm} \= \hspace*{10cm} \\[-3ex]
  \> 2020 - 2021 \> ``Neutron stars as gravitational wave sources'', Sandwich-Scholarship Programme,\\
  \> \> DAAD and MOST (Taiwan), \euro{13,500}. \\
  \> 2017 - 2020 \> Presidential Scholarship of National Tsing Hua University (Taiwan), converted as $\sim$18,700 USD.
\end{tabbing}

\iffalse
\section*{Scientific summary}
\begin{tabular}{ l l r l}
%\hline
%\hline
  Plenary conference talk 			& ... & 1  \\  
  Invited seminar         			& ... & 9  \\
  Conference talk/poster 	& ... & 10  \\
  Number of first author articles 	& ... & 11 \\
  Refereed Articles 				& ... & 17 \\
  Preprints/journal sumissoions 		& ... & 3  \\
  h index (HEP-SPIRES) 				& ... & 10 \\
\end{tabular}
\fi

\section*{Reviewing Activities}
\begin{tabbing}
  \hspace*{5mm} \= \hspace*{2.3cm} \= \hspace*{10cm} \\[-3ex]
  \> {\bf Journals} \> Physical Review D, International Journal of Modern Physics D, European Physical Journal C, \\
  \> \> Monthly Notices of the Royal Astronomical Society
\end{tabbing}




\section*{List of Presentations}
\hspace*{4mm}
{\large \bf \hk{Plenary Talks at Conferences and Workshops}}
\begin{tabbing}
  \hspace*{5mm} \= \hspace*{2cm} \= \hspace*{10cm} \\[-3ex]
  %
  \> {\bf 2022} \> \\[1ex]
  \> Sep 10 \> ``\textbf{Premerger Neutron Star Physics}'', Eleventh Aegean summer school, Syros, Greece.
\end{tabbing}



{\large \bf \hk{Invited Seminars}}
\begin{tabbing}
  \hspace*{5mm} \= \hspace*{2cm} \= \hspace*{10cm} \\[-3ex]
  %
  \> {\bf 2024} \> \\[1ex]
  \> Aug 1 \> ``\textbf{On the finite-size imprints on waveforms of binary neutron star mergers}'', UIUC. \\  
  \> July 11 \> ``\textbf{Imprints of matter and scalar effects on waveforms from binary neutron star mergers}'',\\\
  \> \> online-seminar-in-mathematical-numerical-relativity (\href{https://github.com/Mathematical-Numerical-Relativity/Online-Seminar/wiki}{website}). \\
  \> April 24 \> ``\textbf{Imprints of matter and scalar effects on waveforms from binary neutron star mergers}'',\\
  \> \>  Institute for Gravitational and Subatomic Physics (GRASP), Utrecht University.\\
  \> April 8 \> ``\textbf{(Dynamical) Tidal Effects in the Binary Neutron Star mergers}'',\\
  \> \> AstroParticle and Cosmology laboratory (APC), Paris, France. \\
  %
  \> {\bf 2023} \> \\[1ex]
  \> March 16 \> ``\textbf{Dynamical Scalarization during Neutron Star Mergers in scalar-Gauss-Bonnet Theory}'', \\
  \> \> University of T{\"u}bingen, Germany.\\
  \> February 3 \> ``\textbf{Developing waveform involving dynamical tides}'', \\
  \> \> Academia Sinica, Taipei, Taiwan.\\
  \> February 2 \> ``\textbf{Gravitational Phase Transition in
  Massive Scalar-tensor Theory}'', \\
  \> \> National Center for Theoretical Sciences, Hsinchu, Taiwan.\\
  %
  \> {\bf 2021} \> \\[1ex]
  \> July 27 \>``\textbf{$g$-mode resonances as triggers for precursors of SGRBs}'', \\ 
  \> \> Grav@zon group, Federal University of Pará, Pará, Brazil. \\
  \> Jun 22\>``\textbf{Dynamical formation of scalarized black holes and neutron stars through stellar}\\
  \> \> \textbf{core collapse}'', \\ 
  \> \> cosmo/GW journal club, Johns Hopkins University, Maryland, USA.
\end{tabbing}


{\large \bf \hk{Contributed Talks}}
\begin{tabbing}
  \hspace*{5mm} \= \hspace*{2cm} \= \hspace*{10cm} \\[-3ex]
  %
  \> {\bf 2024} \> \\[1ex]
  \> Oct 9 \> ``\textbf{On the finite-size imprints on waveforms of binary neutron star mergers}'',\\
  \> \> Observatoire de Paris - site de Meudon, France. \\  
  \> Feb 28 \> ``\textbf{Binary neutron star mergers in massive scalar-tensor theory}'',\\
  \> \> Gravity and Cosmology 2024, Yukawa Institute for Theoretical Physics, Kyoto, Japan.\\
  %
  \> {\bf 2023} \> \\[1ex]
  \> Oct 26 \> ``\textbf{Binary neutron star mergers in massive scalar-tensor theory: an
  adiabatic look}'', \\
  \> \> poster, GravityShapePisa 2023, Pisa, Italy.\\
  \> April 5 \> ``\textbf{Dynamical Scalarization during BNS mergers
  in scalar-Gauss-Bonnet}'', \\
  \> \> CoCoNut meeting, Potsdam, Germany.\\
  \> March 22 \> ``\textbf{Packed Message delivered by Tides in
  Binary Neutron Star Mergers}'', \\
  \> \> SMuK2023, Technical University Dresden, Germany.\\
  %
  \> {\bf 2022} \> \\[1ex]
  \> Sep 08 \> ``\textbf{Gravitaional Phase Transition}'', Eleventh Aegean summer school, Syros, Greece.\\
  \> May 16-19 \> ``\textbf{Tidal effects in the pre-merger stage of coalescing binary neutron stars}'', e-poster, \\
  \> \> PHAROS: The multi-messenger physics and astrophysics of neutron stars, Roma, Italy.\\
  \> Mar 3 \> ``\textbf{Resonance shattering as triggers for precursors of SGRBs}'', \\
  \> \> DPG Meeting of the Matter and Cosmos section (SMuK), Heidelberg, Germany.\\
  %
  \> {\bf 2021} \> \\[1ex]
  \> Aug30 - Sep3 \> ``\textbf{Tidal $g$-mode resonances in coalescing binaries of neutron stars as triggers for}\\
  \> \> \textbf{precursor flares of short gamma-ray bursts}'', \\ 
  \> \> DPG Meeting of the Matter and Cosmos section (SMuK), Bad Honnef, Germany. \\
  \> Feb 24-28\>``\textbf{Inverse-Chirp Imprint of GW in Scalar Tensor Theory}'', \\ 
  \> \> 56th Karpacz Winter School in Theoretical Physics, Karpacz, Poland.
\end{tabbing}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section*{Teaching Activities}
\qquad {\Large \bf Teaching assistant}
\begin{tabbing}
  \hspace*{10mm} \= \hspace*{2.8cm} \= \hspace*{10cm} \\[-3ex]
  \> \textbf{At Tsing Hua} \> General Relativity (2016 Fall, 2018 Fall)\\
  \> \> Mathematical Physics (2017-2018) \\
  \> \> Thermal Physics (2016-2017) \\
  \> \> Calculus (2018-2019) \\
  \> \textbf{At T{\"u}bingen} \> Physical Practical (2021 Summer \& Winter)\\
  \> \> Grundkurs Electromagnetism (2022 Summer)
\end{tabbing}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


\section*{Publication Statisitc}
\begin{tabular}{l l l r l}
	& Number of first author articles 	& ... & 11 \\
	& Refereed Articles 					& ... & 18 \\
	& Preprints/journal sumissoions 		& ... & 3  \\
	& Citations 		& ... & 222 \\
	& h index (HEP-SPIRES) 				& ... & 10 \\
\end{tabular}

\section*{First-author refereed/under-review publications}
\begin{enumerate}
	\item \textbf{H.-J. Kuan}, K. Kiuchi, M. Shibata. Tidal Resonance in Binary Neutron Star Inspiral: A High-Precision Study in Numerical Relativity. arXiv:2411.xxxxx.
	%
	\item \textbf{H.-J.~Kuan} and K.~D.~Kokkotas. Last three seconds: Packed message delivered by tides in binary neutron star mergers. \href{https://journals.aps.org/prd/abstract/10.1103/PhysRevD.108.063026}{Phys. Rev. D 108:063026, September 2023}. 
	%
	\item \textbf{H.-J.~Kuan}, K.~V.~Van Aelst, A.~T.~L.~Lam and M.~Shibata. Binary neutron star mergers in massive scalar-tensor theory: Quasiequilibrium states and dynamical enhancement of the scalarization. \href{https://journals.aps.org/prd/abstract/10.1103/PhysRevD.108.064057}{Phys. Rev. D 108:064057, September 2023}.
	%
	\item \textbf{H.-J.~Kuan}, A.~G.~Suvorov and K.~D.~Kokkotas. Measuring spin in coalescing binaries of neutron stars showing double precursors. \href{	https://doi.org/10.1051/0004-6361/202346658}{Astron. Astrophys., 676(2):A59, June 2023}.
	%
	\item \textbf{H.-J.~Kuan}, A.~T.~L.~Lam, D.~D.~Doneva, S.~S.~Yazadjiev, M.~Shibata and K.~Kiuchi. Dynamical scalarization during neutron star mergers in scalar-Gauss-Bonnet theory. \href{https://journals.aps.org/prd/abstract/10.1103/PhysRevD.108.063033}{Phys. Rev. D 108:063033, September 2023}.
	%
	\item (*) \textbf{H.-J.~Kuan} and K.~D.~Kokkotas. $f$-mode imprints on gravitational waves from coalescing binaries involving aligned spinning neutron stars. \href{https://journals.aps.org/prd/abstract/10.1103/PhysRevD.106.064052}{Phys. Rev. D 106:064052, September 2022}.
	%
	\item \textbf{H.-J.~Kuan}, A.~G.~Suvorov, D.~D.~Doneva and S.~S.~Yazadjiev. Gravitational Waves from Accretion-Induced Descalarization in Massive Scalar-Tensor Theory. \href{https://journals.aps.org/prl/abstract/10.1103/PhysRevLett.129.121104}{Phys. Rev. Lett. 129:121104, September 2022}.
	%
	\item \textbf{H.-J.~Kuan}, C.~J.~Kr{\"u}ger, A.~G.~Suvorov and K.~D.~Kokkotas. Constraining equation of state groups from $g$-mode asteroseismology. \href{https://doi.org/10.1093/mnras/stac1101}{MNRAS, 513(3):4045-4056, April 2022}.
	%
	\item \textbf{H.-J.~Kuan}, J.~Singh, D.~D.~Doneva, S.~S.~Yazadjiev, and K.~D.~Kokkotas. Nonlinear evolution and nonuniqueness of scalarized neutron stars. Phys. Rev. D, 104:124013, December 2021. \href{https://doi.org/10.1103/PhysRevD.104.124013}{10.1103/PhysRevD.104.124013}.
	%
	\item  \textbf{H.-J.~Kuan}, A.~G.~Suvorov and K.~D.~Kokkotas. General-relativistic treatment of tidal g-mode resonances in coalescing binaries of neutron stars. II. As triggers for precursor flares of short gamma-ray bursts. \href{https://doi.org/10.1093/mnras/stab2658}{MNRAS, 508(2):1732-1744, December 2021}.
	%
	\item (*) \textbf{H.-J.~Kuan}, D.~D.~Doneva, and S.~S.~Yazadjiev. Dynamical Formation of Scalarized Black Holes and Neutron Stars through Stellar Core Collapse. \href{https://doi.org/10.1103/PhysRevLett.127.161103}{Phys. Rev. Lett., 127:161103, October 2021}.
	%
	\item \textbf{H.-J.~Kuan}, A.~G.~Suvorov, and K.~D.~Kokkotas. General-relativistic treatment of tidal g-mode resonances in coalescing binaries of neutron stars - I. Theoretical framework and crust breaking. \href{https://doi.org/10.1093/mnras/stab1898}{MNRAS, 506(2):2985–2998, September 2021}.
\end{enumerate}



\section*{Second-author refereed/under-review publications}
\begin{enumerate}
	\item (*) A. G. Suvorov, \textbf{H.-J. Kuan}, K. D. Kokkotas. Premerger phenomena in neutron-star binary coalescences. \href{https://arxiv.org/abs/2408.16283}{arXiv:2408.16283 }
	%
	\item A. T.-L. Lam, \textbf{H.-J. Kuan}, M. Shibata, K. Van Aelst, K. Kiuchi. Binary neutron star mergers in massive scalar-tensor theory: Properties of post-merger remnants. \href{https://journals.aps.org/prd/abstract/10.1103/PhysRevD.110.104018}{Phys.Rev.D 110:104018, November 2024}.
	%
	\item V. Brdar, T. Cheng, \textbf{H.-J. Kuan}, and Y.-Y. Li. Magnetar-powered neutrinos and magnetic moment signatures at IceCube. \href{https://iopscience.iop.org/article/10.1088/1475-7516/2024/07/026}{JCAP 07:026, July 2024}. 
	%
	\item A.~G.~Suvorov, \textbf{H.-J.~Kuan}, Alexis Reboul-Salze and K.~D.~Kokkotas. Magnetic amplification in pre-merger neutron stars through resonance-induced magnetorotational instabilities.  \href{https://journals.aps.org/prd/abstract/10.1103/PhysRevD.109.103023}{Phys.Rev.D 109:103023, May 2024}.
	%
	\item A.~G.~Suvorov, \textbf{H.-J.~Kuan} and K.~D.~Kokkotas. Quasi-periodic oscillations in precursor flares via seismic aftershocks from resonant shattering. \href{https://www.aanda.org/articles/aa/full_html/2022/08/aa44082-22/aa44082-22.html}{Astron. Astrophys. 664:A177, August 2022}.
	%
	\item D.~Huang, C.~Q.~Geng, and \textbf{H.-J.~Kuan}. Scalar gravitational wave signals from core collapse in massive scalar-tensor gravity with triple-scalar interactions. \href{https://doi.org/10.1088/1361-6382/ac35ab}{Class. Quant. Grav., 38:245006, November 2021}.
	%
	\item C.~Q.~Geng, \textbf{H.-J.~Kuan}, and L.~W.~Luo. Inverse-chirp imprint of gravitational wave signals in scalar tensor theory. \href{https://doi.org/10.1140/epjc/s10052-020-8359-y}{Eur. Phys. J. C, 80:780, August 2020}.
	%
	\item C.~Q.~Geng, \textbf{H.-J.~Kuan}, and L.~W.~Luo. Viable Constraint on Scalar Field in Scalar-Tensor Theory.	\href{https://doi.org/10.1088/1361-6382/ab86fb}{Class. Quant. Grav., 37:115001, May 2020}.
\end{enumerate}


\section*{Other co-authored refereed/under-review publications}
\begin{enumerate}
	\item A. T.-L. Lam, Yong Gao, \textbf{H.-J. Kuan}, M. Shibata, K. Van Aelst, K. Kiuchi. Accessing universal relations of binary neutron star waveforms in massive scalar-tensor theory. \href{https://arxiv.org/abs/2410.00137 }{arXiv:2410.00137 }
\end{enumerate}


\end{document}


\end{document}


